Wrinkling à la Biot

### 2015-01-25 plis_figures.tex
Split fig:dynamics, panel c in Supplementary. Supplementary method that describe fig:patterns and fig:generations
Insert nonmonotonic Do not use cycle list name=earthy Add time arrow on I(q)

>>>>

\begin{figure}
	\tikzsetnextfilename{generations}
	\input{fig_plis/generations.pgf}%
	\caption{Fourier spectra of binary altitudes of Fig.~\ref{fig:dynamics}a corresponding to primary, secondary and tertiary patterns. Inset: reconstructed binary altitudes at time \SI{2}{\hour}. Scale bars is \SI{1}{\milli\metre}.}%
	\label{fig:generations}%
\end{figure}

\begin{figure*}
	\tikzsetnextfilename{nonmonotonic}
	\input{fig_plis/nonmonotonic.pgf}%
	\caption{Microstructure evolution. (a) Details of confocal images in fully adhesive conditions (left) and with no adhesion on top (right). Scale bar is \SI{10}{\micro\metre}. Arrows indicates the pore size. (b) Corresponding Fourier spectra in second situation and same times. Lines are fits by Eq.~\ref{eq:fractalS}. (c-d) Evolution of susceptibility and fractal dimension in both situations (black line and orange dashed line respectively). Symbols indicates the times of the images in (a).}%
	\label{fig:nonmonotonic}%
\end{figure*}
